---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# whocaresnot

<!-- badges: start -->
<!-- badges: end -->

This package implements a factor mixture model (FMM) based approach to the detection inconsistent responding to multi-item scales including items with different semantic polarity (i.e., reverse-coded items), using OpenMx and requiring minimal user input.

Based on the approach described in:

Arias, V. B., Garrido, L. E., Jenaro, C., Martínez-Molina, A., & Arias, B. (2020). A little garbage in, lots of garbage out: Assessing the impact of careless responding in personality survey data. Behavior Research Methods, 52(6), 2489–2505. https://doi.org/10.3758/s13428-020-01401-8

## Installation

You can install the development version of whocaresnot from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("damiencrone/whocaresnot")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r libraries}
library(whocaresnot)
library(haven)
```

```{r data}
# From https://osf.io/n6krb
dat = read_sav("~/Downloads/raw_data_and_MPlus_code/DATA_SAMPLE_1.sav")
```

```{r specify model}
ov = c(paste0("E", 1:6, "_P"), paste0("E", 1:6, "_N"))
reversed = paste0("E", 1:6, "_N")
model = construct_model(data = dat, ov, reversed)
```

```{r estimate model}
fit = estimate_model(model, try_hard = TRUE)
probs = get_class_assignment_probabilities(fit)
```

```{r}
plot_decision_threshold(probs)
```

```{r}
plot_assignment_probability_distribution(probs)
```

```{r}
head(get_responses(data = dat[, ov], probs))
```
